# SAfeR

__SAfeR__ is an R package that contains a record of crime statistics in the country of South Africa along with functions to easily visualize these statistics. 

## Installation 

You can start using SAfeR after installing it from Github:
```{r}
devtools::install_github("aidaylanan/SAfeR")
```

## Contents

### Data

__SAfeR__ contains a tidy data set of the number of crimes committed in South Africa per province from 2005 to 2015.

### Functionality

*mean_crime()* returns the average number of crimes committed of a certain category, as reported by a provided police station. 

*plotting_crime()* plots the types of crimes per province of a given year. 

*trend_line()* plots the change in crime over the years in a given station and crime category. Category is prompted for after function is run.

*max_crime()* plots the top three crimes reported by a given station during a given year.

## Examples 

Preview of the data set, labeled *crime*:
```{r, echo = FALSE}
head(crime)
```

The types of crimes committed in South Africa in 2010:
```{r}
plotting_crime(2010)
```
